Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-08-30 WSSSPE3/report/WSSSPE3_review.tex
adding CCL URL

The lightning talks were intended to give an opportunity for attendees to
quickly highlight an important issue or a potential solution.
%
\begin{enumerate}
\item \textbf{Benjamin Tovar and Douglas Thain: \textit{Freedom vs.\ Stability:
Facilitating Research Training While Supporting Scientific Research}}. Benjamin
Tovar presented a case study of ``The Cooperative Computing Lab'' at the
University of Notre Dame, which is a small group of individuals whose main tasks
are collaborating with people that have large-scale computing problems,
operating various parallel computer systems, conducting computer science
research, and developing open source software. One of the main challenges they
face is finding a balance between flexibility/training and stability/quality.
Their current solution for ensuring the latter was to add a software engineer
(the presenter) to the existing team of faculty and students, who now also
serves as a ``spring'' between flexibility and stability.

>>>>

The lightning talks were intended to give an opportunity for attendees to
quickly highlight an important issue or a potential solution.
%
\begin{enumerate}
\item \textbf{Benjamin Tovar and Douglas Thain: \textit{Freedom vs.\ Stability:
Facilitating Research Training While Supporting Scientific Research}}. Benjamin
Tovar presented a case study of the Cooperative Computing Lab (CCL)\footnote{\url{http://ccl.cse.nd.edu}} at the
University of Notre Dame, which is a small group of individuals whose main tasks
are collaborating with people that have large-scale computing problems,
operating various parallel computer systems, conducting computer science
research, and developing open source software. One of the main challenges they
face is finding a balance between flexibility/training and stability/quality.
Their current solution for ensuring the latter was to add a software engineer
(the presenter) to the existing team of faculty and students, who now also
serves as a ``spring'' between flexibility and stability.
